Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-03 bbbq_article.tex
Plot SNP conservation in simpler bar plots, fix #186

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_conservation.png}
  \caption{
    Evolutionary conservation of SNPs in TMHs.
  }
  \label{fig:conservation}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_conservation_per_spanner.png}
  \caption{
    Evolutionary conservation of SNPs in TMHs,
    for either single- or multi-spanners
  }
  \label{fig:conservation_per_spanner}
\end{figure}
